Graphs of Mice and Men

### 2016-07-03 Paper/Draft.tex
All results have been added

 To prove this hypothesis, I must proof the following points:
 \begin{itemize}
 \item The algorithm uses distributed representations of concepts.
 \item The algorithm finds relationships between concepts in ontologies.
 \item The algorithm has been compared to the currently best matchers.
 \item The algorithm performs better.
 \end{itemize}

@@

 \subsubsection{Current state} %TODO This bit can use some work
 % Tip: google wie schreef Harry Potter
 Currently, people are not aware of the Semantic Web. Either websites and applications do not use any semantic information, or it is used on the back-end, hidden with other complex programs that users will not understand. So what is the Semantic Web used for nowadays, if at all? In this section, I will list a number of general ways people use Semantic Web technologies as well as specific applications. Note that these are Semantic Web technologies, i.e. technologies that came into existence through Semantic Web research and can eventually be used in the Semantic Web, but currently are not used for the Semantic Web since it does not exist yet.
 \paragraph{}
 Semantic Web systems are currently divided into two groups: the systems that need high accuracy and the ones that need high recall. The first group are deployed in domains that require exact knowledge, whereas the second group are systems that must make available a big amount of data. In the past it was not possible to extract information from texts and other sources automatically, so all systems were hand-crafted and thus highly accurate but very small. This also impacted research, which did not focus on scaling ontologies until recently.
 \paragraph{}
 The group that requires high recall use hand-crafted knowledge bases, created by experts, containing only facts that are accurate, verified and relevant\cite{mika2015schema}. This method of creating a knowledge base does not scale very well and usually consists of fewer than ten thousand facts. Because of this, the knowledge bases are restricted to small domains, including some parts of medicine and cultural heritage\cite{byrne, le2002}.
 \paragraph{}
 For the group that requires a high recall, or in other words a big amount of data, automated methods are required. These methods work fast, parsing thousands of websites a minute, but are inclined to make mistakes. Often, these methods use crowd-sourcing to improve accuracy, using experts or the general public to suggest or check facts\cite{zhou2007}.
 \paragraph{}
 On way the W3C is fighting ambiguity is to ensure very few different languages are used for ontologies and knowledge bases. The main languages W3C endorses are RDF, OWL and SKOS\cite{rdf, owl, skos}. 
 \paragraph{}
 Large ontologies already exist, with the largest, Freebase, boasting almost two billion triples and the three hundred combined Large Open Data databases contain over thirty billion\cite{dbpedia, lod}. The LOD is simply a single alignment over many different knowledge bases.
 \paragraph{}
 Applications include improved web searching, question answering, product comparison, context merging, data integration, decision support, translation, all the way up to the intelligent softbot mentioned earlier. \cite{schreiber, future}
 \paragraph{}
 The many uses of ontology matching show that it is important to research all avenues that might improve ontology matching, as it will have a direct result in many other fields.
 \subsubsection{Technologies}
 %TODO Wil ik dit nog doen?

@@

 There are three main reasons ontologies are used. Firstly, it allows querying languages to optimize the search process. Secondly, it allows expansion of information on a node. Thirdly, it allows for consistency checking a knowledge base. Lastly, it allows merging of knowledge bases.

@@

@@

@@

 \subsection{Word representation} \label{w2v}
 An important area of research in Natural Language Processing is the representation of words. The most obvious representation is the collection of characters humans are used to. However, this is not useful for computers as these characters do not say anything about the meaning of the words, nor is it a representation that computers can quickly do calculations on.
 \paragraph{}
 Many different representations have been proposed. The main purpose of word representations in NLP is to represent the meaning of the word. One way to represent a word is the term frequency. This representation counts the number of occurrences of a word per document in a set of documents. The resulting vector of occurrence counts is then used to represent the words. Since the documents have a subject, there is some meaning embedded in the vector representation. However, the representation is very sparse and the semantics or meaning of the word are not captured very well. Also, the method requires many discrete documents to train on, which are not available in ontology matching.
 \paragraph{}
 The rest of this subsection will describe the latest word representation model which has very interesting results in NLP. It will cover the history and the most recent advances that are relevant to this study.

@@

 \subsection{Used technology}
 \subsubsection{Factorie} \label{factorie}
 Factorie is a toolkit that contains a number of tools which includes word-embedding models \cite{git-factorie}. \cite{w2v}.
 \paragraph{}
 Factorie provides a number of utilities for writing an algorithm in the shape of abstract classes with existing functionality, namely IO, parallelisation, quick parsing and command line argument parsing. It also provides example implementations and programs. Factorie is written in scala, a language that has been gaining popularity recently and interfaces with java. See \cite{scala}. 
 \paragraph{}
 The automated IO allows for quick reading in of the data set and secure saving of the trained model. The file reading is quicker than a naive CSV parser would allow for, and thus enabled quicker training of the models. This meant less time is used and more time can be used for experimenting and improving the algorithm. Saving the different models allows for model comparison after all models have been trained, which means new investigations can be performed after conclusions have been drawn from earlier investigations, without having to retrain all models. This also allows multiple models to be trained during a period where the experimenter is absent, after which he can still manually investigate the models.
 \paragraph{}
 Parallelisation can massively improve training speed. It allows an algorithm to update its model for multiple learning instances at the same time, thus reducing the time needed by the number of instances it can process simultaneously. The number of parallel processes differs per device but modern personal computers already boast 8 parallel processors.
 \paragraph{}
 Since I investigate many different implementations of the same algorithm, it should be easy to switch between these implementations at run-time without much effort. Command line parsing allows for this to happen, and thus improves experimentation ease.

@@

@@

 \subsection{Considered implementations}

@@

 %TODO F-pieken aanwijzen. Dan confidence vs F-measure bespreken in interpretation.
 % Wat is de threshold van AML?
 % Extra rij met baseline literal string matcher
 \subsection{Precision versus recall}
  \subsubsection{Mice and men data}
  \begin{figure}[H]
   \centering
   \includegraphics[width=\textwidth]{plots/untrained_ROC}
   \caption[Precision-recall curve untrained mice]{The precision and recall trade-off for the results of the untrained Node2vec. $AP = 0.04194$}
   \label{ROC_untrained}
  \end{figure}

  \begin{figure}[H]
   \centering
   \includegraphics[width=\textwidth]{plots/Generic_ROC}
   \caption[Precision-recall curve pre-trained mice]{The precision and recall trade-off for the results of the Word2vec algorithm. $AP: 0.04636$}
   \label{ROC_generic}
  \end{figure}

  \begin{figure}[H]
   \centering
   \includegraphics[width=\textwidth]{plots/trained_ROC}
   \caption[Precision-recall curve trained mice model]{The precision and recall trade-off for the results of the bidirectional Node2vec. $AP = 0.04198$}
   \label{ROC_trained}
  \end{figure}

  \begin{figure}[H]
   \centering
   \includegraphics[width=\textwidth]{plots/Alternative_ROC}
   \caption[Precision-recall curve DeepWalk mice]{The precision and recall trade-off for the results of the alternative DeepWalk algorithm. $AP = 0.04193$}
   \label{ROC_alternative}
  \end{figure}
   \subsubsection{Medical data}
   TBD

  \subsection{F-score}
  \begin{table}[H]
  \caption[$F_1$ mice]{The $F_1$-scores for the different matchers for the mice dataset compared to the result of AML at OAEI 2015 \cite{oaei2015}}
  \label{fscores}
  \begin{tabular}{l|ll}
  \multirow{2}{*}{\textbf{Matcher}} & \multicolumn{2}{c}{\textbf{$F_1$-score}} \\
  & Anatomy & Medical\\
  \hline
  Label Match & 0.6926 & 0.4905 \\
  Random & 0.6926 & 0.4905 \\
  Generic & 0.6372 & 0.3874 \\
  Bidirectional & 0.8432 & 0.4946 \\
  Deepwalk &  & 0.4906 \\
  Alternative & 0.6372 & 0.4905 \\
  \textbf{AML ensemble} & \textbf{0.94} & \textbf{0.81} \\ %http://disi.unitn.it/~pavel/om2015/
  %papers/om2015_proceedings.pdf#page=125
  \end{tabular}
  \end{table}
  %\subsection{Jaccard}
  %TBD
  \subsection{Examples to illustrate the differences}
  TBD

@@

 The goal of this study was to answer the research question from Section \ref{researchquestion}:
 \begin{center}
 \textit{
 Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing matchers?
 }
 \end{center}

 To answer this question I have examined the following points from Section \ref{hypotheses}:

\paragraph{The algorithm uses distributed representations of concepts}
\paragraph{The algorithm finds relationships between concepts in ontologies}
\paragraph{The algorithm has been compared to the currently best matchers}
\paragraph{The algorithm performs better}
 I performed empirical research where I made the algorithm, applied it to different datasets and compared the results with existing methods.

 Because the last point is not true, the answer is not in agreement with my hypothesis from Section \ref{hypotheses}:

The results from all the different evaluation measures are in agreement. From those results we can conclude the following:

@@

 \subsection{Discussion}
 %TODO gooi weg wat niet meer waar is
  This study shows that the algorithm of McCallum et al as shown in \cite{mccallumweblecture} does not help improve the results of ontology alignment over the straightforward baseline of simply pairing labels based on their syntactic similarity in the area of ontology matching.

@@

  %In de presentatie zegt hij ook dat hij niet gaat proberen dingen meteen op elkaar te matchen maar gewoon alles houdt zoals het gelezen is/in de KB staat. Toch haalt hij goede resultaten met rule discovery e.d.
 \subsection{Future research}

 \subsection{Discarded implementations}

>>>>

 To prove this hypothesis, I must proof the following points:
 \begin{itemize}
 \item The algorithm uses distributed representations of concepts.
 \item The algorithm finds relationships between concepts in ontologies.
 \item The algorithm performs better.
 \end{itemize}

@@

 \subsubsection{Current state} %TODO This bit can use some work
 Zijn alle losse technologien er al? Ja. Hoe? RDF en OWL worden al gebruikt. Google heeft al betere search door Knowledge gRaph (hummingbird) plaatje etc...
 Door lack of adoption is het er niet.

 % Tip: google wie schreef Harry Potter
 Currently, people are not aware of the Semantic Web. Either websites and applications do not use any semantic information, or it is used on the back-end, hidden with other complex programs that users will not understand. So what is the Semantic Web used for nowadays, if at all? In this section, I will list a number of general ways people use Semantic Web technologies as well as specific applications. Note that these are Semantic Web technologies, i.e. technologies that came into existence through Semantic Web research and can eventually be used in the Semantic Web, but currently are not used for the Semantic Web since it does not exist yet.
 \paragraph{}
 Semantic Web systems are currently divided into two groups: the systems that need high accuracy and the ones that need high recall. The first group are deployed in domains that require exact knowledge, whereas the second group are systems that must make available a big amount of data. In the past it was not possible to extract information from texts and other sources automatically, so all systems were hand-crafted and thus highly accurate but very small. This also impacted research, which did not focus on scaling ontologies until recently.
 \paragraph{}
 The group that requires high recall use hand-crafted knowledge bases, created by experts, containing only facts that are accurate, verified and relevant\cite{mika2015schema}. This method of creating a knowledge base does not scale very well and usually consists of fewer than ten thousand facts. Because of this, the knowledge bases are restricted to small domains, including some parts of medicine and cultural heritage\cite{byrne, le2002}.
 \paragraph{}
 For the group that requires a high recall, or in other words a big amount of data, automated methods are required. These methods work fast, parsing thousands of websites a minute, but are inclined to make mistakes. Often, these methods use crowd-sourcing to improve accuracy, using experts or the general public to suggest or check facts\cite{zhou2007}.
 \paragraph{}
 On way the W3C is fighting ambiguity is to ensure very few different languages are used for ontologies and knowledge bases. The main languages W3C endorses are RDF, OWL and SKOS\cite{rdf, owl, skos}. 
 \paragraph{}
 Large ontologies already exist, with the largest, Freebase, boasting almost two billion triples and the three hundred combined Large Open Data databases contain over thirty billion\cite{dbpedia, lod}. The LOD is simply a single alignment over many different knowledge bases.
 \paragraph{}
 Applications include improved web searching, question answering, product comparison, context merging, data integration, decision support, translation, all the way up to the intelligent softbot mentioned earlier. \cite{schreiber, future}
 \paragraph{}
 The many uses of ontology matching show that it is important to research all avenues that might improve ontology matching, as it will have a direct result in many other fields.

@@

 There are four main reasons ontologies are used. Firstly, it allows querying languages to optimize the search process. Secondly, it allows expansion of information on a node. Thirdly, it allows for consistency checking a knowledge base. Lastly, it allows merging of knowledge bases.

@@

 %TODO Meer voorbeelden meer plaatjes (uit hun papers). Eerst ga ik uitleggen..

@@

 %TODO Cite en in discussion of w2v dit kan helpen. Zo niet: weg

@@

 \subsection{Word representation} \label{w2v}
 % Meer McCallum noemen. 80 plaatjes %TODO
 An important area of research in Natural Language Processing is the representation of words. The most obvious representation is the collection of characters humans are used to. However, this is not useful for computers as these characters do not say anything about the meaning of the words, nor is it a representation that computers can quickly do calculations on.
 \paragraph{}
 Many different representations have been proposed. The main purpose of word representations in NLP is to represent the meaning of the word. One way to represent a word is the term frequency. This representation counts the number of occurrences of a word per document in a set of documents. The resulting vector of occurrence counts is then used to represent the words. Since the documents have a subject, there is some meaning embedded in the vector representation. However, the representation is very sparse and the semantics or meaning of the word are not captured very well. Also, the method requires many discrete documents to train on, which are not available in ontology matching.
 \paragraph{}
 The rest of this subsection will describe the latest word representation model which has very interesting results in NLP. It will cover the history and the most recent advances that are relevant to this study.

@@

 \subsection{Used technology}
 \subsubsection{Factorie} \label{factorie}
 Factorie is a toolkit that contains a number of tools which includes word-embedding models \cite{git-factorie, w2v}.
 \paragraph{}
 Factorie provides a number of utilities for writing an algorithm in the shape of abstract classes with existing functionality, namely IO, parallelisation, quick parsing and command line argument parsing. It also provides example implementations and programs. Factorie is written in scala, a language that has been gaining popularity recently and interfaces with java. See \cite{scala}. 
 \paragraph{}
 The automated IO allows for quick reading in of the data set and secure saving of the trained model. The file reading is quicker than a naive CSV parser would allow for, and thus enabled quicker training of the models. This meant less time is used and more time can be used for experimenting and improving the algorithm. Saving the different models allows for model comparison after all models have been trained, which means new investigations can be performed after conclusions have been drawn from earlier investigations, without having to retrain all models. This also allows multiple models to be trained during a period where the experimenter is absent, after which he can still manually investigate the models.
 \paragraph{}
 Parallelisation can massively improve training speed. It allows an algorithm to update its model for multiple learning instances at the same time, thus reducing the time needed by the number of instances it can process simultaneously. The number of parallel processes differs per device but modern personal computers already boast 8 parallel processors.
 \paragraph{}
 Since I investigate many different implementations of the same algorithm, it should be easy to switch between these implementations at run-time without much effort. Command line parsing allows for this to happen, and thus improves experimentation ease.

@@

 %TODO AML toevoegen

@@

 \subsection{Algorithms}
 %TODO Move sommige naar discussions
 %TODO per algorithme uitleggen: hoe het werkt. Waarom gekozen. Plaatjes. Volgorde van kiezen (ik denk dat deze beter past) en bij resultaten bespreken of deze volgorde klopt.

@@

 %TODO F-pieken aanwijzen. Dan confidence vs F-measure bespreken in interpretation.
 % Wat is de threshold van AML?
 % Extra rij met baseline literal string matcher
 \subsection{Precision versus recall}
  \subsubsection{Mice and men data}
  \begin{figure}[H]
   \centering
   \includegraphics[width=\textwidth]{plots/untrained_ROC}
   \caption[Precision-recall curve untrained mice]{The precision and recall trade-off for the results of the untrained Node2vec.}
   \label{ROC_untrained}
  \end{figure}

  \begin{figure}[H]

 \begin{subfigure}{.3\textwidth}
   \centering
   \includegraphics[width=\textwidth]{plots/Generic_ROC}
   \caption[Precision-recall curve pre-trained mice]{Pretrained Word2vec algorithm.}
   \label{ROC_generic}
   \end{subfigure}
 \begin{subfigure}{.3\textwidth}
   \centering
   \includegraphics[width=\textwidth]{plots/trained_ROC}
   \caption[Precision-recall curve trained mice model]{bidirectional Node2vec.}
   \label{ROC_trained}
  \end{subfigure}
 \begin{subfigure}{.3\textwidth}
   \centering
   \includegraphics[width=\textwidth]{plots/Alternative_ROC}
   \caption[Precision-recall curve DeepWalk mice]{Alternative DeepWalk algorithm.}
   \label{ROC_alternative}
  \end{subfigure}
  \caption{Precision-recall trade-off curve for the results of three more algorithms.}
  \end{figure}
   \subsubsection{Medical data}
   TBD

  \subsection{F-score}
  \begin{table}[H]
  \caption[$F_1$ mice]{The $F_1$-scores for the different matchers for the mice dataset compared to the result of AML at OAEI 2015 \cite{oaei2015}}
  \label{fscores}
  \begin{tabular}{l|ll}
  \multirow{2}{*}{\textbf{Matcher}} & \multicolumn{2}{c}{\textbf{$F_1$-score}} \\
  & Anatomy & Medical\\
  \hline
  Label Match & 0.6926 & 0.4905 \\
  Random & 0.6926 & 0.4905 \\
  Generic & 0.6372 & 0.3874 \\
  Bidirectional & 0.8432 & 0.4946 \\
  Deepwalk & 0.6926 & 0.4906 \\
  Alternative & 0.6372 & 0.4905 \\
  \textbf{AML ensemble} & \textbf{0.94} & \textbf{0.81} \\ %http://disi.unitn.it/~pavel/om2015/
  %papers/om2015_proceedings.pdf#page=125
  \end{tabular}
  \end{table}
  %\subsection{Jaccard}
  %TBD
  \subsection{Examples to illustrate the differences}
  TBD

@@

 The goal of this study was to answer the research question from Section \ref{researchquestion}:
 \begin{center}
 \textit{
 Can distributed representations of concepts be used to find relationships between concepts in ontologies better than the best existing matcher?
 } % Zelfde als sectie hypothese?
 \end{center}

 To answer this question I have examined the following points from Section \ref{hypotheses} for every algorithm (Pre-trained Word2vec, DeepWalk, Node2vec):

\paragraph{The algorithm uses distributed representations of concepts} %TODO In de uitleg van het algoritme duidelijk maken dat dit zo is.

Yes. They all use distributed representations since they all convert words into vectors:
\begin{description} \item[pre-trained Word2vec] ... 
\item[] ...
\end{description}
\paragraph{The algorithm finds relationships between concepts in ontologies} %TODO In de system check duidelijk maken.

This is correct as the inputs are always two ontologies and the output is always a set relationships between the ontologies.
\paragraph{The algorithm performs better}

Not yet.

I compared the results of the algorithms with AML, the best existing matcher. All algorithms perform below AML. However, there is potential for better performance as we can see in Section \ref{discussion}.
\paragraph{}
 Because the last point is not true, the answer is not in agreement with my hypothesis from Section \ref{hypotheses}.
 \paragraph{}
The results from all the different evaluation measures are in agreement. From those results we can conclude the following:

@@

 %TODO Arjen vragen dit te bekijken

 \subsection{Discussion} \label{discussion}
 %TODO gooi weg wat niet meer waar is

  This study shows that the algorithm of McCallum et al as shown in \cite{mccallumweblecture} does not help improve the results of ontology alignment over the straightforward baseline of simply pairing labels based on their syntactic similarity in the area of ontology matching.

@@

  %In de presentatie zegt hij ook dat hij niet gaat proberen dingen meteen op elkaar te matchen maar gewoon alles houdt zoals het gelezen is/in de KB staat. Toch haalt hij goede resultaten met rule discovery e.d.

  % Het was wel gelukt als ik ... (wat eerst future research was)

 \subsection{Discarded algorithms}
